### 2018-04-19 results.tex
update

Some aspects of Fig.~\ref{fig:clusters} are worth discussing. Although in most plots all four clusters are clearly distinguishable, there are others in which that is not the case. In the C5-C9 and C7-C9 combinations in the 3-feature analysis, for instance, the excellent cluster has a limited presence. This is due to the influence of the lower C9 values (see Fig.~\ref{fig:data-box-plot}) on the correlations with C5 and C7. This is not necessarily a bad thing, as it helps to understand the different relationships between the various GOF metrics. In the best of cases, the combinations C1-C2 and C5-C8 in the 2- and 4-feature analysis, for instance, exhibit an almost perfect proportionality between the metrics. That means either one of the metrics in those combinations is redundant. Relationships with redundant features are those where knowledge about one of the features provides a direct view into the other. On the other hand, the combination C1-C7 in the 2-feature analysis presents an example of an irrelevant feature. We say C1 is irrelevant because it provides no insight about the outcome of C7 or that of the clusters. Identifying subspaces with redundant and irrelevant features is important because, on the one hand, the former help reduce the number of necessary features, while on the other hand, the latter can essentially be discarded because of their weak contribution to the decision making process \citep{Dy_2004_MLR}.

@@

In total, the clustering process results in 816, 1253, 879 and 76 data samples for the poor, fair, good and excellent classes, respectively. These groups are shown in Fig.~\ref{fig:count-classes}. As it can be seen in this figure, the number of samples in the excellent class is significantly less than those in the poor, fair, and good classes. Therefore, before moving on with the decision tree analysis, it is necessary to resample the subset of the excellent class. We used the oversampling approach described in the previous section. We replicated data from the excellent class 
\myrevision{through random selection of data from that class until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes} with the dashed line. This oversampling is considered as a $\times$10 factor.} 
\myremove{randomly by a $\times$10 factor until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes} with the dashed line.} 
% By common standards, an oversample rate of $\times$10 is considered acceptable \citep{Weiss_2003_JAIR}. 
\mychange{According to \citet{Weiss_2003_JAIR}, an oversample rate of $\times$10 is considered to be acceptable in this type of data processing.}
(Arguably, we could have as well undersampled the fair class, but we deemed that unnecessary. Instead, we used a \myremove{strong} \myrevision{heavy} pruning process to prevent overfitting.) Once this process was completed we went on with the decision tree analysis.

@@

A low participation does not necessarily mean that a given metric is not important. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean, in the context of GOF validation \myrevision{for engineering applications} , is that in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as energy (C8) are much more decisive in \myrevision{narrowing eleven validation metrics into fewer numbers in order to get the same categorization as all eleven metrics}  \myremove{reaching an accurate conclusion about validation quality} than the duration (C11).

@@

%\begin{table}[t]
%	\centering
%	\caption{Metrics data analysis participation in select trees (in percent)}
%	\label{tab:participation}
%	\small
%	\begin{tabular}{lrrrr}
%	Metric 	& T1 	& T2	& T3 	& T66 	\\ 
%	\hline
%	C1 		& --	& --	& -- 	& 1.5	\\
%	C2 		& -- 	& --	& -- 	& 0.5	\\
%	C3 		& -- 	& -- 	& -- 	& 9.6	\\
%	\rowcolor{light-light-gray}
%	C4 		& 46.8	& 52.4	& 60.2	& 100.0	\\
%	\rowcolor{light-light-gray}
%	C5 		& -- 	& 21.5	& 21.5	& 72.2	\\
%	\rowcolor{light-light-gray}
%	C6 		& -- 	& -- 	& 37.0	& 56.3	\\
%	C7 		& -- 	& -- 	& -- 	& 19.4	\\
%	\rowcolor{light-light-gray}
%	C8 		& 100.0	& 100.0	& 100.0	& 100.0	\\
%	C9 		& -- 	& -- 	& --	& 23.8	\\
%	C10		& -- 	& -- 	& -- 	& 22.2	\\
%	C11		& -- 	& -- 	& -- 	& -- 	\\
%	\hline
%	\end{tabular}
%\end{table}

\begin{table}[t]
	\centering
	\caption{Metrics data analysis participation in select trees (in percent). \myrevision{Stars represent the trees with same complexity in pruning process, however, not exact tree structures.}}
	\label{tab:participation}
	\small
	\myrevision{
	\begin{tabular}{lrrrrrrrrrrrr}
	Metric 	& T1 	& T2	& T3 	& T66  & T1* 	& T2*	& T3* 	& T66*  & T1* 	& T2*	& T3* 	& T66* 	\\ 
	\hline
	&\multicolumn{4}{c}{Including C8} & \multicolumn{4}{c}{Without C8}&  \multicolumn{4}{c}{Without C5 and C8}\\
	\hline
	C1 		& --	& --	& -- 	& 1.5 & --	& --	& -- 	& --- & --	& --	& -- 	& --	\\
	C2 		& -- 	& --	& -- 	& 0.5 & --	& --	& -- 	& 2.27 & --	& --	& -- 	& --	\\
	C3 		& -- 	& -- 	& -- 	& 9.6 & --	& --	& -- 	& 53.22 & --	& 60.35	& 61.19 	& 99.11	\\
	\rowcolor{light-light-gray}
	C4 		& 46.8	& 52.4	& 60.2	& 100.0  & 44.35	& 81.77	& 81.77 	& 83.20 & 47.44	& 48.67	& 80.54 	& 54.64	\\
	\rowcolor{light-light-gray}
	C5 		& -- 	& 21.5	& 21.5	& 72.2 & 100.0	& 100.0	& 100.0 	& 100.0 & --	& --	& -- 	& --	\\
	\rowcolor{light-light-gray}
	C6 		& -- 	& -- 	& 37.0	& 56.3 & 58.65	& 63.51	& 62.77 	& 82.39 & 100.0	& 100	& 100 	& 100\\
	C7 		& -- 	& -- 	& -- 	& 19.4 & --	& --	& -- 	& 32.37 & --	& --	& -- 	& 43.24	\\
	\rowcolor{light-light-gray}
	C8 		& 100.0	& 100.0	& 100.0	& 100.0 & --	& --	& -- 	& --	 & --	& --	& -- 	& --\\
	C9 		& -- 	& -- 	& --	& 23.8 & --	& --	& -- 	& 48.63 & --	& --	& -- 	& 72.22	\\
	C10		& -- 	& -- 	& -- 	& 22.2 & --	& --	& -- 	& 24.93 & --	& --	& -- 	& 20.46	\\
	C11		& -- 	& -- 	& -- 	& -- 	    & --	& --	& -- 	& --- & --	& --	& -- 	& 8.09\\
	\hline
	\end{tabular}
	}
\end{table}

>>>>

Some aspects of Fig.~\ref{fig:clusters} are worth discussing. Although in most plots all four clusters are clearly distinguishable, there are others in which that is not the case. In 
% the C5-C9 and C7-C9 combinations in 
\change{the combinations in}
the 3-feature analysis, for instance, the excellent cluster has a limited presence. This is due to the influence of the lower C9 values (see Fig.~\ref{fig:data-box-plot}) on the correlations with C5 and C7. This is not necessarily a bad thing, as it helps to understand the different relationships between the various GOF metrics. In the best of cases, the combinations C1-C2 and C5-C8 in the 2- and 4-feature analysis, for instance, exhibit an almost perfect proportionality between the metrics. That means either one of the metrics in those combinations is redundant. Relationships with redundant features are those where knowledge about one of the features provides a direct view into the other. On the other hand, the combination C1-C7 in the 2-feature analysis presents an example of an irrelevant feature. We say C1 is irrelevant because it provides no insight about the outcome of C7 or that of the clusters. Identifying subspaces with redundant and irrelevant features is important because, on the one hand, the former help reduce the number of necessary features, while on the other hand, the latter can essentially be discarded because of their weak contribution to the decision making process \citep{Dy_2004_MLR}.

@@

In total, the clustering process results in 816, 1253, 879 and 76 data samples for the poor, fair, good and excellent classes, respectively. These groups are shown in Fig.~\ref{fig:count-classes}. As it can be seen in this figure, the number of samples in the excellent class is significantly less than those in the poor, fair, and good classes. Therefore, before moving on with the decision tree analysis, it is necessary to resample the subset of the excellent class. We used the oversampling approach described in the previous section. We replicated data from the excellent class 
\myrevision{through random selection of data from that class until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes} with the dashed line. This oversampling is considered as a $\times$10 factor.} 
\myremove{randomly by a $\times$10 factor until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes} with the dashed line.} 
% By common standards, an oversample rate of $\times$10 is considered acceptable \citep{Weiss_2003_JAIR}. 
\change{According to \citet{Weiss_2003_JAIR}, an oversample rate of $\times$10 is considered to be acceptable in this type of data processing.}
(Arguably, we could have as well undersampled the fair class, but we deemed that unnecessary. Instead, we used a \change{heavy} pruning process to prevent overfitting.) Once this process was completed we went on with the decision tree analysis.

@@

A low participation does not necessarily mean that a given metric is not important. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean \change{is that, in the context of this particular set of 11 metrics, in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as energy (C8) are much more influential in the final result than the duration (C11). This, of course, is done under the assumption that one seeks to narrow the selection of metrics without loss of insight about the outcome of the validation process when compared to the outcome obtained with the whole suite of the eleven metrics used here.}

% Original:
% A low participation does not necessarily mean that a given metric is not important. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean, in the context of GOF validation, is that in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as energy (C8) are much more decisive in reaching an accurate conclusion about validation quality than the duration (C11).

% Naeem suggestion:
% A low participation does not necessarily mean that a given metric is not important. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean, in the context of GOF validation for engineering applications, is that in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as energy (C8) are much more decisive in narrowing eleven validation metrics into fewer numbers in order to get the same categorization as all eleven metrics than the duration (C11).

@@

\input{tab-partition}
